An accelerated algorithm for finding efficient solutions in multiobjective problems with black-box multiextremal criteria\thanks{This work was supported by the Russian Science Foundation, project No. 21-11-00204.}

### 2022-07-01 2022/OPTIMA/paper.tex
fix table

\begin{table}
\caption{\textcolor{red}{ Results of the experiment with multidimensional MCO problems.}}
\centering
\begin{tabular}{cccccccccc} \hline
Series& $N$& $k$& Pareto & RALR-DA & OMOPSO & SPEA2 & SMPSO & IBEA & NSGAII   \\ \hline
1& 2&	2 & 6.62 & 6.44 & 5.93 & 5.88 & 5.71 & 5.65 & 5.61 \\ 
2& 4&	2 &  5.04 & 4.71 & 4.53 & 4.45 & 4.39 & 4.39 & 4.37 \\ 
3& 2&	4 &  23.89 & 23.52 & 22.87 & 22.80 & 22.53 & 20.68 & 19.82 \\ \hline
\end{tabular}
\label{tab4_6}
\end{table}

>>>>

\begin{table}
\caption{\textcolor{red}{ Results of the experiment with multidimensional MCO problems.}}
\centering
\begin{tabular}{cccccccccc} \hline
Series& $N$& $k$& Pareto & RALR-DA & OMOPSO &SMPSO & NSGAII & IBEA & SPEA2  \\ \hline
1& 2&	2 & 6.62 & 6.44 & 5.93 & 5.88 & 5.71 & 5.65 & 5.61 \\ 
2& 4&	2 & 5.04 & 4.71 & 4.45 & 4.37 & 4.39 & 4.39 & 4.53 \\ 
3& 2&	4 &  23.89 & 23.52 & 22.87 & 22.53 & 19.82 & 20.68 & 22.80 \\ \hline
\end{tabular}
\label{tab4_6}
\end{table}
